Topological order in the quantum dimer-pentamer model

### 2015-09-16 qdpm_paper.tex
pulling
added U(1) winding number measured on qdpm, a figure of gray heat map of dimer correlations, qdpm example config, table moddifications

@@

    \subsection{Liquid}

@@

>>>>

            \begin{figure}[htpb]
                \centering
                \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
                \caption{The $U(1)$ winding number as measured in the QDPM on a $8\times8$ lattice
                with a dimer to pentamer move fraction (need a name for this fraction HERE) of 0.5.}
                \label{fig:u1_wind_qdpm}
            \end{figure}

@@

    \subsection{Liquid}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale (actualy data) of the dimer corelation between the dimer in the upper
        left corner and other dimers on a $16\times16$ lattice.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}

@@

    \begin{table*}[htpb]
    \setlength\tabcolsep{0.3cm}
        \centering
        \caption{$\Delta \tau = 150$}
        \label{tab:label}
        \begin{tabular}{l l l l}
            \hline\hline
                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
            \hline
            frac 1.0    &  &  & \\
            $8\times8$  &                       &                       &                            \\
            $12\times12$&                       &                       &                            \\
            $16\times16$&                       &                       &                            \\
            $18\times18$&                       &                       &                            \\
            \hline
            frac 0.9    &  &  & \\
            $8\times8$  & $3.5(3)\times10^{-3}$ & $1.02(8)\times10^{-3}$&  $3.07(4)\times10^{-3}$    \\
            $12\times12$&                       &                       &                            \\
            $16\times16$&                       &                       &                            \\
            $18\times18$&                       &                       &                            \\
            \hline
            frac 0.5    &  &  & \\
            $8\times8$  & $1.(8)\times10^{-2}$  &  $5.(6)\times10^{-4}$ & $1.7(5)\times10^{-2}$      \\
            $12\times12$& $1.4(8)\times10^{-2}$ &                       &                            \\
            $16\times16$&                       &                       &                            \\
            $18\times18$&                       &                       &                            \\
        \end{tabular}
    \end{table*}
